---
title: "summarize-project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{summarize-project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(projectlog)
```

This vignette explains how you can leverage `projectlog` to create a summary of all the milestones of your project.

## 1. A scenario where you have used `projectlog` from the start of your project

If you used `projectlog` to initiate your project repository, a top-level `README.Rmd` file was automatically created.
This `README.Rmd` file by default contains the function `generate_milestone_overview()`, which creates a bulleted overview of all the milestones that you logged along the way using `log_milestones()`.
Simply reknitting the `README.Rmd` file at any point will regenerate the milestones to include your latest changes.

Running `generate_milestone_overview()`, either manually or by knitting the `README.Rmd` file, will do three things behind the scenes:

1. All the tags that were created on GitHub as a result of using `log_milestones()` are extracted from GitHub, and matched to the metadata that were provided when logging the milestone (e.g., date, description, code, etc.).

2. For each milestone that signals first-time access to data, an .R file is generated under `.projectlog/`. This .R file contains the code that was used to read in the data, and contains a link to the GitHub commit associated with the first-time data access.

3. A bulleted overview of each milestone is created, containing relevant meta data.

## 2. A scenario where you have started using `projectlog` later in project

If you did not use `projectlog` to initiate your project, chances are you do not have a `README.Rmd` file containing the code to generate the milestones.
If so, you can manually create this README file using `add_project_readme()`.
This README will by default contain the `generate_milestone_overview()` function (see section 1).
Alternatively, you can manually run `generate_milestone_overview()` and include the output anywhere you'd like.
Note that by adding `copy = TRUE`, the overview of milestones will automatically be copied to your clipboard.

It might happen that you did not log certain milestones, for example, because you started using projectlog later in your project, or because you forgot to do so at some point.
TBD

