---
title: "Project name"
output: github_document
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=F, echo=F}
library(fs)
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

<!-- Below is a basic set-up for a README file that will help readers become familiar with the structure of your project and how to use it. You can remove and/or add information and headers as you see fit for your particular project.-->

This repository contains data, code, and output for a manuscript entitled "XXX" submitted at XXX.

# 1. Project history

## 1. Directory Structure {#structure}

The names of each folder are intended to be self-explanatory.
There are seven top-level folders to organize the inputs and outputs of this project:

1.  `project_log/`: Folder containing meta-information of the project history as generated by the `projectlog` package (see below).
2.  `preregistrations/`: The preregistration(s) for the analyses done prior to Stage 1 submission.
3.  `supplement/`: a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.
4.  `scripts/`: R-scripts that read, analyze, and produce all analysis objects.
5.  `materials`: All materials that were used in this project. 
6.  `data/`: Folder containing raw data. 
7.  `analysis_objects/`: Folder containing outputs of the analysis scripts.
8.  `codebooks/`: lists of variable names, labels, and value labels (where applicable).

Below is a simple visualization of the full directory structure.

```{r}
fs::dir_tree(".", regexp = "^README|.Rproj$|log$|tex$|_files|groundhog|data/.*|analysis_objects/(test_set.csv|training_set.csv|tasks_clean.RData)", invert = T)
```

Each of the top-level folders are explained in more detail below:

## Project log


## Preregistrations

This directory contains the preregistrations for this project.

## Supplement

## Data Processing Scripts

## Data {#data}

## Analysis objects

## Codebooks

These are lists of variable names, labels, and value labels (where applicable) (see [data](#data) below).

## How to reproduce this repository {#reproduce}

